---
title: "pollution-report"
author: "Omer Cofman"
date: "April 27, 2016"
output: pdf_document
---

This is a global dataset of 1571 locations where surface manta tows were conducted.

Samples were divided into 4 size categories. Weights and particle counts were recorded for each category.

Since the 4th categories of both weight and particle counts were mostly NA values, they were gone in the data cleaning operation.

More attributes I cleaned out are Date, Sea State, Source (scientist), Info and Comments.

We are left with the Latitude, Longitude, and 3 size categories by weights and particle counts.

Attribute Information:

1.  Latitude
2.  Longitude
3.  CD1: numeric, particle counts for debris between .335-.999 mm, units: [1/km^2]
4.  CD2: numeric, particle counts for debris between 1.00-4.75 mm, units: [1/km^2]
5.  CD3: numeric, particle counts for debris between 4.75-200 mm, units: [1/km^2]
3.  WD1: numeric, particle weight for debris between .335-.999 mm, units: [g/km^2]
4.  WD2: numeric, particle weight for debris between 1.00-4.75 mm, units: [g/km^2]
5.  WD3: numeric, particle weight for debris between 4.75-200 mm, units: [g/km^2]

```{r, echo=FALSE, results="hide", warning=FALSE, message=FALSE}
require(RCurl)

#get the data
data.uri = "https://raw.githubusercontent.com/AndrewSan/ex2-Plastic-Marine-Pollution-Global-Dataset/master/pollution.csv"
data = read.csv(data.uri)

```

Let's see some data

```{r}
head(data);
```

As you can see in the next chunk, most of the values are zero

```{r}
summary(data)
```

Now we will display the debris on the world map.

Each couple of maps corresponds to one of the particle counts columns.

The size of the mark on the map is in proportion to the average size in mm and the weight of the debris

CD1*WD1/.677

```{r, echo=F, warning=F,message=F}
require(ggmap)
par(mfrow=c(1,2))
map1 = get_map(location=c(lon=100+(mean(data$Longitude)),lat=mean(data$Latitude)),zoom=2,maptype="watercolor",scale=2)
map2 = get_map(location=c(lon=(mean(data$Longitude)-85),lat=mean(data$Latitude)),zoom=2,maptype="watercolor",scale=2)
#cd1
ggmap(map1) + geom_point(data=data,aes(x=Longitude,y=Latitude,alph=0.1),size=log(data$cd1*data$wd1/.677/100),colour="darkred") + guides(fill=F,alpha=F,size=F)
ggmap(map2) + geom_point(data=data,aes(x=Longitude,y=Latitude,alph=0.1),size=log(data$cd1*data$wd1/.677/100),colour="darkred") + guides(fill=F,alpha=F,size=F)
```



CD2*WD2/2.875

```{r, echo=F, warning=F,message=F}
ggmap(map1) + geom_point(data=data,aes(x=Longitude,y=Latitude,alph=0.1),size=log(data$cd2*data$wd2/2.875/100),colour="darkred") + guides(fill=F,alpha=F,size=F)
ggmap(map2) + geom_point(data=data,aes(x=Longitude,y=Latitude,alph=0.1),size=log(data$cd2*data$wd2/2.875/100),colour="darkred") + guides(fill=F,alpha=F,size=F)
```



CD3*WD3/100

```{r, echo=F, warning=F,message=F}
ggmap(map1) + geom_point(data=data,aes(x=Longitude,y=Latitude,alph=0.1),size=log(data$cd3*data$wd3/100/100),colour="darkred") + guides(fill=F,alpha=F,size=F)
ggmap(map2) + geom_point(data=data,aes(x=Longitude,y=Latitude,alph=0.1),size=log(data$cd3*data$wd3/100/100),colour="darkred") + guides(fill=F,alpha=F,size=F)
```


We learn that CD2 objects (1.00-4.75mm) are most of the volume of junk in the oceans.

Now lets see what we can learn from splitting the data by longitude

1. from 150 to 200
2. from 50 to 150
3. from 30 to 50
4. from -80 to 30
5. from -200 to -80

```{r}
data.1 = data[data$Longitude<200 & data$Longitude>150,]
data.2 = data[data$Longitude<150 & data$Longitude>50,]
data.3 = data[data$Longitude<50 & data$Longitude>30,]
data.4 = data[data$Longitude<30 & data$Longitude>-80,]
data.5 = data[data$Longitude<-80 & data$Longitude>-200,]
mean(data.1$cd1*data.1$wd1/.677 + data.1$cd2*data.1$wd2/2.875 + data.1$cd3*data.1$wd3/100)
mean(data.2$cd1*data.2$wd1/.677 + data.2$cd2*data.2$wd2/2.875 + data.2$cd3*data.2$wd3/100)
mean(data.3$cd1*data.3$wd1/.677 + data.3$cd2*data.3$wd2/2.875 + data.3$cd3*data.3$wd3/100)
mean(data.4$cd1*data.4$wd1/.677 + data.4$cd2*data.4$wd2/2.875 + data.4$cd3*data.4$wd3/100)
mean(data.5$cd1*data.5$wd1/.677 + data.5$cd2*data.5$wd2/2.875 + data.5$cd3*data.5$wd3/100)
```

We see that the fith area (from -200 to -80) is the dirtiest.

Unsurprisingly, it has the most of CD2 type debris

```{r}
sum(data.1$cd2)
sum(data.2$cd2)
sum(data.3$cd2)
sum(data.4$cd2)
sum(data.5$cd2)
```









